The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-10 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

(ref:cap-Fig1) "Winning percentage of NBA home teams in the playoffs since 2010, the green line denotes .500"
```{r Fig1, echo=FALSE, fig.cap = " (ref:cap-Fig1)", fig.align='center'}
winyear <- cbind(winpct, years)
winyear <- as.data.frame(winyear)
highlight <- data.frame(winpct = .482, years = 2020)
ggplot(winyear, aes(x=years, y=winpct))+ 
      geom_point()+
      geom_point(data=highlight, 
             aes(x=years, y=winpct), 
             color='red')+
      scale_x_continuous(name = "Year", breaks = years, labels = years)+
      scale_y_continuous(limits = c(0.4, 0.8))+
      geom_hline(aes(yintercept = 0.5), color = "green")+
      geom_text(aes(label=winpct), hjust=0, vjust=-1, size=2)
```

@@

Figure \@ref(fig:Fig3) shows home shooting for two pointers, three pointers and
free throws for 2020(top) vs. 2017-19(bottom). The histograms appear to be fairly
similarly distributed between 2020 and 2017-19. Likewise, Figure \@ref(fig:Fig4),
shows the same data except for away teams. Just like Figure \@ref(fig:Fig3),
Figure \@ref(fig:Fig4) histograms don’t show any obvious differences. The normality
of the distributions in both Figure \@ref(fig:Fig3) and Figure \@ref(fig:Fig4) are
important for meeting the required assumptions for statistical analysis.

>>>>

(ref:cap-Fig1) Winning percentage of NBA home teams in the playoffs since 2010, the green line denotes .500
```{r Fig1, echo=FALSE, fig.cap = " (ref:cap-Fig1)", fig.align='center'}
winyear <- cbind(winpct, years)
winyear <- as.data.frame(winyear)
highlight <- data.frame(winpct = .482, years = 2020)
ggplot(winyear, aes(x=years, y=winpct))+ 
      geom_point()+
      geom_point(data=highlight, 
             aes(x=years, y=winpct), 
             color='red')+
      scale_x_continuous(name = "Year", breaks = years, labels = years)+
      scale_y_continuous(limits = c(0.4, 0.8))+
      geom_hline(aes(yintercept = 0.5), color = "green")+
      geom_text(aes(label=winpct), hjust=0, vjust=-1, size=2)
```

@@

Figure \@ref(fig:Fig3) shows home shooting for two pointers, three pointers and
free throws for 2020 (top) vs. 2017-19 (bottom). The histograms appear to be fairly
similarly distributed between 2020 and 2017-19. Likewise, Figure \@ref(fig:Fig4),
shows the same data except for away teams. Just like Figure \@ref(fig:Fig3),
Figure \@ref(fig:Fig4) histograms don’t show any obvious differences. The normality
of the distributions in both Figure \@ref(fig:Fig3) and Figure \@ref(fig:Fig4) are
important for meeting the required assumptions for statistical analysis.
